\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-17 paper/paper 2/dc-2015.tex
abstract

\maketitle
\vspace{-3em}
\section*{Abstract}
In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation of constraints and validation of RDF data on these constraints are developed. Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
To support the work, a comprehensive, community-driven database has been created where case studies, use cases, requirements and solutions are collected. Based on this database,
we published by today 81 types of constraints that are required by various stakeholders for data applications. We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled. 
Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for Description Set Profiles.
In this paper, we generalize from the experience of implementing DSP by introducing an abstraction layer that is able to describe any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly. 
We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages, simplifies the actual implementation of new languages and supports the transformation of semantically equivalent constraints across constraint languages.

@@

\emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints. The Pellet ICV\footnote{\url{http://clarkparsia.com/pellet/icv}} is a proof-of-concept extension for the OWL 2 DL reasoner \emph{Pellet} \cite{sirin2007pellet}. Stardog ICV\footnote{\url{http://docs.stardog.com/#_validating_constraints}} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL 2, or SWRL \cite{Horrocks04}.

>>>>

\maketitle
\vspace{-3em}
\section*{Abstract}
In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation of constraints and validation of RDF data on these constraints are developed. Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
To support the work, a comprehensive, community-driven database has been created where case studies, use cases, requirements and solutions are collected. Based on this database,
we published by today 81 types of constraints that are required by various stakeholders for data applications. We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled. 
Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for \textcolor{red}{the Web Ontology Language in its current version 2 and }Description Set Profiles.
In this paper, we generalize from the experience of implementing \textcolor{red}{OWL 2 and} DSP by introducing an abstraction layer that is able to describe \textcolor{red}{constraints of} any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly. 
We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages, simplifies the actual implementation of new languages, and supports the transformation of semantically equivalent constraints across constraint languages.

@@

\tb{ToDo Thomas: OWL 2}
\emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints. The Pellet ICV\footnote{\url{http://clarkparsia.com/pellet/icv}} is a proof-of-concept extension for the OWL 2 DL reasoner \emph{Pellet} \cite{sirin2007pellet}. Stardog ICV\footnote{\url{http://docs.stardog.com/#_validating_constraints}} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL 2, or SWRL \cite{Horrocks04}.
